---
title: "Third Assignment"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
Education_and_Internet <- read_excel("~/Desktop/Education and Internet.xlsx")
View(Education_and_Internet)

```

## Asignment 3
The main goal of this third assignment is to gather web based data from at least two sources, merge the data sets, conduct basic descriptive and some inferential statistics on the data to address a relevant research question and briefly describe the results including with dynamically generated tables and figures. 




Purpose: Gather, clean, and (begin to) analyse data
Deadline: 11 November
You will submit a GitHub repo that:
- Gathers web-based data from at least two sources. Cleans and merges the data so that it is ready for statistical analyses.
- Conducts basic descriptive statistics with the data to address a relevant research question. Could include inferential stats.
- Briefly describes the results including with dynamically generated tables and figures.
- Has a write up of 1,500 words maximum that describes the data gathering and analysis, It also will use literate programming




```{r cars}

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
