---
title: "third_repo"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Asignment 3
Purpose: Gather, clean, and (begin to) analyse data
Deadline: 11 November
You will submit a GitHub repo that:
- Gathers web-based data from at least two sources. Cleans and merges the data so that it is ready for statistical analyses.
- Conducts basic descriptive statistics with the data to address a relevant research question. Could include inferential stats.
- Briefly describes the results including with dynamically generated tables and figures.
- Has a write up of 1,500 words maximum that describes the data gathering and analysis, It also will use literate programming




```{r cars}

library(readxl)
Data_Education_and_Internet_Access <- read_excel("~/Desktop/third_repo/Data Education and Internet Access.xlsx")
View(Data_Education_and_Internet_Access)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
